Parsing Tweets into Universal Dependencies

### 2017-09-30 paper.tex
Noah

We release our system at.

\nascomment{not clear to me:  did we reannotate the POS corpus?  was
  that automatic or manual?  I wasn't sure what to do with the POS
  section below.}
\yjcomment{we re-annotated the POS. In one way, Gimple's POS is not very
consistent with UD POS. In another way, 2,500 new tweets were annotated
from scratch and they didn't have Gimple's tags.}

@@

\nascomment{need to introduce this section and explain the structure.
I'm not crazy about what I have now, but I like it better than what
we had before, which seemed to keep repeating the same ideas in
different contexts.  the flow still seems wrong; we start by talking
about dependencies, then take a detour to POS, then come back to
dependencies.}
\subsection{Background: \textsc{Tweebank}}

@@

Another important difference is in tokenization.  UD calls for more
aggressive tokenization than that used by
\newcite{gimpel-EtAl:2011:ACL-HLT2011}, which followed
\newcite{ICWSM101540}.  In particular, they opted out of tokenizing
contractions and possessives, introducing new parts of speech
instead.\footnote{These tags only accounted for 2.7\% of tokens,
  leading to concerns about data sparseness in tagging and all
  downstream analyses.}  For us, these tokens must be split, but
universal parts of speech can be applied.

@@

\paragraph{Acronym abbreviations.}  How should we syntactically
analyze acronym tokens like \emph{idc}
(abbreviating ``I don't care'') and \emph{rn} (``right now'')?  Should
they be decomposed into their component words, and if so should those
words be ``normalized'' into explicitly spelled out intermediate
forms? We follow \citet{kong-EtAl:2014:EMNLP2014} and annotate their
syntax as a single word without normalization. Their syntactic functions
are decided according to their context.
\nascomment{explain what we do, and include how this is
	similar to or different from Kong et al}\yjcomment{done.}

\citet{eisenstein:2013:NAACL-HLT} studied the necessity of normalization
in social media text and pointed that such normalization is problematic.
Our solution to the syntax of abbreviations is in the same spirit with
his work. Further study shows that the abbreviations which clearly carry
syntactic functions only make 0.06\% tokens in our dataset, which
also indicates it's unnecessary to normalize text in social media.
\nascomment{maybe we owe citations to
  \cite{finin-EtAl:2010:MTURK,eisenstein:2013:NAACL-HLT} here?  maybe
  better papers to cite}

\paragraph{Non-syntactic tokens.}  
\begin{table}
\centering
\small
\begin{tabular}{rcc}
\% & syntactic & non-syntactic \\ \hline
emoticons & 0.25 & 0.95 \\
RT & 0.14 & 2.49\\
hashtag & 1.02 & 1.24 \\
URL & 0.67 & 2.38 \\
truncated words & 0 & 0.49 \\
 \hline
 sum & 2.08 & 7.55 \\
\end{tabular}
\caption{Proportion of non-syntactic tokens in the annotation.}\label{tbl:non-synt-prop}
\end{table}
The major characteristic that distinguishes tweets from standard texts is that
there are large proportion of tokens that don't carry any syntactic functions.
In our annotation, there are five types of non-syntactic tokens which include
sentiment emoticons, retweet markers, topical hashtags, referential URLs, and
truncated words. Figure \ref{fig:non-syn-toks} illustrates examples of
these non-syntactic tokens. In the sense of part of speech, emoticons are tagged
as \emph{symbol} ({\tt SYM}) by following the UD guidelines. For other 4 types of
non-syntactic tokens, they generally have the \emph{other} (\texttt{X})
part of speech. In our annotation, these five types of tokens make more than
7.5\% of all tokens and detailed statistics can be found in Table \ref{tbl:non-synt-prop}.
\nascomment{in latex source I've commented out a paragraph about
	truncated content.  it's not clear to me what the nonsyntactic
	tokens are, when that happens}\yjcomment{i've put truncated words here.}

@@

\nascomment{I'm confused about (1) how we define non-syntactic tokens
  (what are the criteria) and (2) whether this is something we kick
  over to POS annotation}
\yjcomment{I've put the definition of non-syntactic tokens there.}

@@

\nascomment{explain our conventions and how
  they relate to Kong and to UD.  in the draft before, we said that we
had conventions, and Kong didn't, but we didn't really say what ours were.}
\yjcomment{The bullet points describe our convention for non-syntactic tokens.}

@@

\begin{figure*}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			Perfect \& \textcolor{red}{\bf $\heart$} \& \textcolor{orange}{\bf RT} \& @coldplay \& : \& Fix \& You \& from \& the \& back \& \textcolor{gray}{\bf \#ColdplayMinneapolis} \& \textcolor{blue}{\bf http://bit.ly/2dj2WCl} \& Nice \& \textcolor{cyan}{\bf p} \& ...\\
			\tiny ADJ \&\tiny SYM \&\tiny X \&\tiny X \&\tiny PUNCT \&\tiny VERB \&\tiny NOUN \&\tiny ADP \&\tiny DET \&\tiny NOUN \&\tiny X \&\tiny X \& \tiny ADJ \& \tiny X \& \tiny PUNCT \\
		\end{deptext}
		\deproot{1}{root}
		\depedge[edge unit distance=1em]{1}{2}{discourse}
		\deproot{6}{root}
		\depedge[edge unit distance=1em]{6}{3}{discourse}
		\depedge[edge unit distance=1em]{3}{4}{discourse}
		\depedge[edge unit distance=1em]{3}{5}{punct}
		\depedge[edge unit distance=1em]{6}{7}{obj}
		\depedge[edge unit distance=0.8em]{6}{10}{obl}
		\depedge[edge unit distance=1em]{10}{8}{case}
		\depedge[edge unit distance=1em]{10}{9}{det}
		\depedge[edge unit distance=0.8em]{6}{11}{discourse}
		\depedge[edge unit distance=0.8em]{6}{12}{list}
		\deproot{13}{root}		
		\depedge[edge unit distance=0.8em]{13}{14}{discourse}
		\depedge[edge unit distance=0.8em]{13}{15}{punct}
	\end{dependency}
	\caption{A example tweet contains major non-syntactic tokens, with
		\textcolor{red}{sentiment emoticon},
		\textcolor{orange}{retweet marker},
		\textcolor{gray}{topical hashtag},
		\textcolor{blue}{referential URL}, and
		\textcolor{cyan}{truncated word}.}\label{fig:non-syn-toks}
\end{figure*}

\begin{figure*}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			@username \& its \& \#awesome \& u \& gonna \& $\heart$ \& it \& Chk \& out \& our \& cooool \& project \& on \& http:// \& + \& RT \& pls\\
			\tiny PROPN \& \tiny PRON \& \tiny ADJ \& \tiny PRON \& \tiny VERB \& \tiny VERB \& \tiny PRON \& \tiny VERB \& \tiny ADP \& \tiny PRON \& \tiny ADJ \& \tiny NOUN \& \tiny ADP \& \tiny X \& \tiny SYM \& \tiny VERB\& \tiny INTJ\\
		\end{deptext}
		\deproot{3}{root}
		\depedge[edge unit distance=1em]{3}{1}{vocative}
		\depedge[edge unit distance=1em]{3}{2}{nsubj}
		\depedge[edge unit distance=1em]{3}{5}{parataxis}
		\depedge[edge unit distance=1em]{5}{4}{nsubj}
		\depedge[edge unit distance=1em]{5}{6}{xcomp}
		\depedge[edge unit distance=1em]{6}{7}{obj}
		\depedge[edge unit distance=0.7em]{3}{8}{parataxis}
		\depedge[edge unit distance=1em]{8}{9}{compound:prt}
		\depedge[edge unit distance=0.7em]{8}{12}{obj}
		\depedge[edge unit distance=1em]{12}{10}{nmod:poss}
		\depedge[edge unit distance=1em]{12}{11}{amod}
		\depedge[edge unit distance=1em]{12}{14}{nmod}
		\depedge[edge unit distance=1em]{14}{13}{case}
		\depedge[edge unit distance=0.45em]{8}{16}{conj}
		\depedge[edge unit distance=1em]{16}{15}{cc}
		\depedge[edge unit distance=0.35em]{3}{17}{discourse}
	\end{dependency}
	\caption{An example tweet with informal but syntactic tokens.}\label{fig:informal-toks}
\end{figure*}

@@

\newcite{kong-EtAl:2014:EMNLP2014} proposed an additional
preprocessing step, \emph{token selection}, in their annotation process.
They required the annotators to first select the non-syntactic
tokens and exclude them from the final dependencies annotation.
%  \nascomment{confusing.  were they removed or
%  just labeled as non-syntactic and then excluded from the tree?  I
%  think they were not actually removed, and were still available,
%  e.g., for defining features of the input for parsing}
In order to keep our annotation conventions in line with UD norms,
we include non-syntactic tokens in our annotation following the
convention above. Compared with \citet{kong-EtAl:2014:EMNLP2014},
we also gave a clear definition of non-syntactic tokens, which help
us avoid confusion.
\nascomment{say what it is, and what they attach to, and clarify that
  the annotators didn't do this manually (I think)}

@@

\paragraph{Vocative at-mentions.}  Another idiomatic construction on
Twitter is an at-mention %(followed by a colon \nascomment{?})
as a sign that a tweet is a reply to a tweet by the mentioned user.  We
treat these at-mentions as vocative expressions, labeling them as
\emph{proper noun} (\texttt{PROPN}) and attaching them to the
following predicate with the label \emph{vocative} (see Figure \ref{fig:informal-toks} for an example).  \nascomment{need an example.} \yjcomment{done.}

@@

\subsection{\sc Tweebank v2}
Following the guideline mentioned above, we create a new annotated Twitter treebank, which we call {\sc Tweebank v2}.

\subsubsection{Data Collection}
{\sc Tweebank v2} is built on the original data of {\sc Tweebank v1} (Kong et al., 2014, 639 tweets), along with additional 201 tweets sampled from \newcite{gimpel-EtAl:2011:ACL-HLT2011} and 2,500 tweets sampled  from the Twitter stream from Feb. 2017 to Jul. 2017.
The latter data source consists 147.4M English tweets which are filtered by {\it lang} attribute in the tweet JSON and {\it langid.py}\footnote{\url{https://github.com/saffsd/langid.py}} toolkit.
%The tweet source of Tweebank V2 consists of three parts. 
%The first is the original Tweebank created by~\cite{kong-EtAl:2014:EMNLP2014}, denoted as Tweebank V1.  There are 639 unique tweets in the training data of Tweebank V1, and 201 unique tweets in the data set. All of the unique tweets in Tweebank V1 are included in Tweebank V2.
%The second are 210 tweets from POS-tagged Twitter corpus of \newcite{owoputi-EtAl:2013:NAACL-HLT}, denoted as Tweebank V1 Dev. It was initially created as a development set of Tweebank V1 for hyperparameter tuning.
%Tweebank V1 Dev comprises were equally sampled from two data set, OCT27 (tweets sampled from a particular day, October 27, 2010) and DAILY 547 (one random English tweet per day from January 2011 through June 2012, 547 tweets in total). We should note that all of the Tweebank V1 tweets were also drawn from OCT27 and DAILY547, and the new tweets we extracted are not in the Tweebank V1.
%The third are 2500 tweets from the Twitter streams from February 2017 to July 2017 from ArchiveTeam,\footnote{https://archive.org} which we call Feb\_Jul\_16 corpus. The Twitter streams are in Spritzer version, which provides a 1\% random sample of public tweets everyday, and the tweets are in twitter JSON format. 
%There are xxx tweets in all the streams. We filtered them with \textit{lang} attribute in \textit{user} and used \textit{langid.py}\footnote{https://github.com/saffsd/langid.py} to pick out English tweets, which ends in xxx tweets in English. Then we sampled 2500 tweets roughly equally from these months.

\subsubsection{Annotation Process}
The whole annotation process contains three stages.
In the first stage, 18 researchers worked on the {\sc Tweebank v1}
proportion and created the initial annotation in one day
following our guideline. Both the guideline and annotation
were further refined by the authors of this paper to increase
the coverage of our guideline and solve inconsistency between
different annotators. In the second stage, a postagger and
parser are trained on the annotated data from the first stage,
and automatically analyze the sampled 2,500 tweets and the authors
of this paper manually correct the parsed data. Finally, an extra
layer of word-level normalization was manually annotated.

\begin{figure}
\centering
\small
\begin{dependency}[edge slant=2, text only label, label style=above]
	\begin{deptext}
		Olympic \& gold \& medallist \& whipped \& by \& John \& Fisher \\
	\end{deptext}
	\deproot{3}{root}
	\depedge[edge unit distance=1em]{3}{1}{amod}
    \depedge[edge unit distance=1em]{3}{2}{compound}
    \depedge[edge unit distance=1em]{3}{4}{acl}
    \depedge[edge unit distance=1em]{4}{6}{obl}
    \depedge[edge unit distance=1em]{6}{5}{case}
    \depedge[edge unit distance=1em]{6}{7}{flat}
	\deproot[edge below]{4}{root}
%	\depedge[edge below, edge unit distance=1em]{3}{1}{amod}
%	\depedge[edge below, edge unit distance=1em]{3}{2}{compound}
	\depedge[edge below, edge unit distance=1em]{4}{3}{nsubj}
%	\depedge[edge below, edge unit distance=1em]{4}{6}{obl}
%	\depedge[edge below, edge unit distance=1em]{6}{5}{case}
%	\depedge[edge below, edge unit distance=1em]{6}{7}{flat}
\end{dependency}
\caption{An example of disagreement when annotating tweets with ellipsis.}\label{fig:disagree}
\end{figure}

We report the inter-annotator agreement between the annotators
in the second stage. The agreement on POS is 96.61\%, the unlabeled
dependency agreement is 88.75\% and the labeled dependency agreement
is 84.31\%. Further analysis shows the major disagreements on POS
involve entity names (30.57\%) and topical hashtags (18.11\%).
Taking the example in Figure \ref{fig:non-syn-toks}, ``Fix you'' can
be understood as a verbal phrase but also as the name of the Coldplay's
single and tagged as proper noun. The disagreements on dependencies
annotation come in several different ways. One of these disagreements
is resulted by the ellipsis as shown in Figure \ref{fig:disagree}.
Due to the absence of auxiliary verb, this tweet can either be treated
as a nominal phrase modified by a clause or a sentence with auxiliary
verb missing.

@@

We present a pipeline system to parse tweets into universal dependency.

\subsection{Tokenizer}
Tokenization, as the initial step of many NLP tasks, is non-trivial for
Twitter domain \cite{ICWSM101540}. Due to the informal nature, tweets
present several cases which are unconventional for traditional
toeknization module, like hashtags, at-mentions and emoticons. Some of
them are even ambiguous without understanding their contexts. For example,
the asterisk (*) in {\it 4*3} works as a symbol of multiplying and
delimiter of tokens {\it 4 * 3}; but for the asterisk (*) in {\it SH*T}
works as a mask for censorship, should not be treated as a delimiter.

Considering the complexity of tweets tokenization, instead of manually
crafting rules, we propose to deal with tweets tokenization with a 
character-level bidirectional LSTM (bi-LSTM) sequence-labeling model.
Our model takes the raw sentence and tag each character in this 
sentence as whether it is the beginning of a word.

\paragraph{Experimental Results}

\begin{table}[t]
	\centering
	\small
	\begin{tabular}{rc}
		\hline
		\it System & F \\
		\hline
		Stanford Tokenizer & 96.6 \\
		Twokenizer & 94.4 \\
		UD pipe v1.2 & 94.7 \\
		UD pipe v1.2 (re-trained) & 97.3 \\
		Our Tokenizer & \bf 98.3 \\
		\hline
	\end{tabular}
	\caption{The tokenization results.}\label{tbl:tok-result}
\end{table}

We test our tokenizer on Tweebank v2 test set.
F-score was used to evaluate the tokenization accuracy.
Our model was trained on a merge of UD\_English and Tweebank v2 training data.
Table \ref{tbl:tok-result} shows the tokenization results along with comparison with other tokenizers.
Our bi-LSTM tokenizer achieves the best accuracy among all these tokenizers.
By comparing the rule-based group to the model-based group, we can see the model-based ones generally outperform the rule-based tokenizers, which shows the necessity of using statistical model for tweet tokenization.

\subsection{POS-Tagger}

Part-of-Speech tagging for tweets has been studied in previous literals \cite{ritter-EtAl:2011:EMNLP,gimpel-EtAl:2011:ACL-HLT2011,owoputi-EtAl:2013:NAACL-HLT,gui-EtAl:2017:EMNLP20172}.
We use the postagger of \newcite{owoputi-EtAl:2013:NAACL-HLT}.

\paragraph{Experimental Results}

\begin{table}[t]
	\centering
	\small
	\begin{tabular}{rc}
		\hline
		\it System & P \\
		\hline
		Stanford Postagger & 65.6 \\
		Stanford Postagger (re-train) & 90.4 \\
		UD pipe v1.2 & 78.7 \\
		UD pipe v1.2 (re-trained) & 83.8 \\
		bi-LSTM & 91.8 \\
		ARK Tagger & \bf 95.1 \\
		\hline
	\end{tabular}
	\caption{The POS tagging result on gold tokenization.}\label{tbl:pos-result}
\end{table}

\begin{table}[t]
	\centering
	\small
	\begin{tabular}{rc}
		\hline
		\it System & F \\
		\hline
		Stanford Tokenizer & 92.0 \\
		Our Tokenizer & 93.6 \\
		\hline
	\end{tabular}
	\caption{The POS tagging result on automatic tokenization. The POS tagger we used is from Owoput et al., 2013.}\label{tbl:pos-result-vs-tok}
\end{table}

We test several different POS taggers on Tweebank v2.
We also study the influence of tokenization on POS-tagging by evaluating the model's performance on automatically tokenized data.
This result is shown in Table \ref{tbl:pos-result-vs-tok}.

>>>>

We release our dataset and our system as open-source software at
\url{http://anonymized}.

\nascomment{I didn't do anything significant to the intro.  for every
  example, make clear whether it's ``real'' or contrived.}

@@

\nascomment{need to introduce this section and explain the structure.}

\subsection{Background: \textsc{Tweebank}}

@@

Another important difference is in tokenization.  UD calls for more
aggressive tokenization than that used by
\newcite{gimpel-EtAl:2011:ACL-HLT2011}, which followed the rule-based
system  introduced by 
\newcite{ICWSM101540}.  In particular, they opted out of tokenizing
contractions and possessives, introducing new parts of speech
instead.\footnote{These tags only accounted for 2.7\% of tokens,
  leading to concerns about data sparseness in tagging and all
  downstream analyses.}  For us, these tokens must be split, but
universal parts of speech can be applied.

@@

\paragraph{Acronym abbreviations.}  How should we syntactically
analyze acronym tokens like \emph{idc}
(abbreviating ``I don't care'') and \emph{rn} (``right now'')?  Should
they be decomposed into their component words, and if so should those
words be ``normalized'' into explicitly spelled out intermediate
forms? We follow \citet{kong-EtAl:2014:EMNLP2014} and annotate their
syntax as a single word without normalization. Their syntactic functions
are decided according to their context.

\citet{eisenstein:2013:NAACL-HLT} studied the necessity of normalization
in social media text and pointed that such normalization is problematic.
Our solution to the syntax of abbreviations follows the spirit of his argument. Because abbreviations which clearly carry
syntactic functions only constitute 0.06\% of the tokens in our
dataset, we believe that normalization is an unnecessarily complicated step.
\nascomment{maybe we owe citations to
  \cite{finin-EtAl:2010:MTURK,eisenstein:2013:NAACL-HLT} here?  maybe
  better papers to cite}

\paragraph{Non-syntactic tokens.}  
\begin{table}
\centering
\begin{tabular}{lrr}
\multicolumn{2}{r}{syntactic (\%)} & non-syntactic (\%)\\ \hline
emoticons & 0.25 & 0.95 \\
RT & 0.14 & 2.49\\
hashtag & 1.02 & 1.24 \\
URL & 0.67 & 2.38 \\
truncated words & 0.00 & 0.49 \\
 \hline
 total & 2.08 & 7.55 \\
\end{tabular}
\caption{Proportion of non-syntactic tokens in the annotation.}\label{tbl:non-synt-prop}
\end{table}
The major characteristic that distinguishes tweets from standard texts is that
there are large proportion of tokens that don't carry any syntactic function.
In our annotation, there are five types of non-syntactic tokens: 
sentiment emoticons, retweet markers, topical hashtags, referential URLs, and
truncated words. Figure \ref{fig:non-syn-toks} illustrates examples of
these non-syntactic tokens.  As discussed above, these are generally
tagged with the \emph{other} (\texttt{X}) part of speech, except
emoticons, which are tagged as \emph{symbol} (\texttt{SYM}).  In our annotation, 
7.5\% of all tokens are non-syntactic; detailed statistics can be found in Table \ref{tbl:non-synt-prop}.

@@

@@

@@

\begin{figure*}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			Perfect \& \textcolor{red}{\bf $\heart$} \& \textcolor{orange}{\bf RT} \& @coldplay \& : \& Fix \& You \& from \& the \& back \& \textcolor{gray}{\bf \#ColdplayMinneapolis} \& \textcolor{blue}{\bf http://bit.ly/2dj2WCl} \& Nice \& \textcolor{cyan}{\bf p} \& ...\\
			\tiny ADJ \&\tiny SYM \&\tiny X \&\tiny X \&\tiny PUNCT \&\tiny VERB \&\tiny NOUN \&\tiny ADP \&\tiny DET \&\tiny NOUN \&\tiny X \&\tiny X \& \tiny ADJ \& \tiny X \& \tiny PUNCT \\
		\end{deptext}
		\deproot{1}{root}
		\depedge[edge unit distance=1em]{1}{2}{discourse}
		\deproot{6}{root}
		\depedge[edge unit distance=1em]{6}{3}{discourse}
		\depedge[edge unit distance=1em]{3}{4}{discourse}
		\depedge[edge unit distance=1em]{3}{5}{punct}
		\depedge[edge unit distance=1em]{6}{7}{obj}
		\depedge[edge unit distance=0.8em]{6}{10}{obl}
		\depedge[edge unit distance=1em]{10}{8}{case}
		\depedge[edge unit distance=1em]{10}{9}{det}
		\depedge[edge unit distance=0.8em]{6}{11}{discourse}
		\depedge[edge unit distance=0.8em]{6}{12}{list}
		\deproot{13}{root}		
		\depedge[edge unit distance=0.8em]{13}{14}{discourse}
		\depedge[edge unit distance=0.8em]{13}{15}{punct}
	\end{dependency}
	\caption{An example tweet that contains non-syntactic tokens:
		\textcolor{red}{sentiment emoticon},
		\textcolor{orange}{retweet marker},
		\textcolor{gray}{topical hashtag},
		\textcolor{blue}{referential URL}, and
		\textcolor{cyan}{truncated word}.}\label{fig:non-syn-toks}
\end{figure*}

\begin{figure*}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			@username \& its \& \#awesome \& u \& gonna \& $\heart$ \& it \& Chk \& out \& our \& cooool \& project \& on \& http:// \& + \& RT \& pls\\
			\tiny PROPN \& \tiny PRON \& \tiny ADJ \& \tiny PRON \& \tiny VERB \& \tiny VERB \& \tiny PRON \& \tiny VERB \& \tiny ADP \& \tiny PRON \& \tiny ADJ \& \tiny NOUN \& \tiny ADP \& \tiny X \& \tiny SYM \& \tiny VERB\& \tiny INTJ\\
		\end{deptext}
		\deproot{3}{root}
		\depedge[edge unit distance=1em]{3}{1}{vocative}
		\depedge[edge unit distance=1em]{3}{2}{nsubj}
		\depedge[edge unit distance=1em]{3}{5}{parataxis}
		\depedge[edge unit distance=1em]{5}{4}{nsubj}
		\depedge[edge unit distance=1em]{5}{6}{xcomp}
		\depedge[edge unit distance=1em]{6}{7}{obj}
		\depedge[edge unit distance=0.7em]{3}{8}{parataxis}
		\depedge[edge unit distance=1em]{8}{9}{compound:prt}
		\depedge[edge unit distance=0.7em]{8}{12}{obj}
		\depedge[edge unit distance=1em]{12}{10}{nmod:poss}
		\depedge[edge unit distance=1em]{12}{11}{amod}
		\depedge[edge unit distance=0.6em]{8}{14}{obl}
		\depedge[edge unit distance=1em]{14}{13}{case}
		\depedge[edge unit distance=0.55em]{8}{16}{conj}
		\depedge[edge unit distance=1em]{16}{15}{cc}
		\depedge[edge unit distance=0.37em]{3}{17}{discourse}
	\end{dependency}
	\caption{An example tweet with informal but syntactic tokens.}\label{fig:informal-toks}
\end{figure*}

@@

\newcite{kong-EtAl:2014:EMNLP2014} proposed an additional
preprocessing step, \emph{token selection}, in their annotation process.
They required the annotators to first select the non-syntactic
tokens and exclude them from the final dependencies annotation.
%  \nascomment{confusing.  were they removed or
%  just labeled as non-syntactic and then excluded from the tree?  I
%  think they were not actually removed, and were still available,
%  e.g., for defining features of the input for parsing}
In order to keep our annotation conventions in line with UD norms,
we include non-syntactic tokens in our annotation following the
convention above. Compared with \citet{kong-EtAl:2014:EMNLP2014},
we also gave a clear definition of non-syntactic tokens, which helped
us avoid confusion during annotation.

@@

\paragraph{Vocative at-mentions.}  Another idiomatic construction on
Twitter is an at-mention %(followed by a colon \nascomment{?})
as a sign that a tweet is a reply to a tweet by the mentioned user.  We
treat these at-mentions as vocative expressions, labeling them as
\emph{proper noun} (\texttt{PROPN}) and attaching them to the
following predicate with the label \emph{vocative} (see Figure \ref{fig:informal-toks} for an example).

@@

\subsection{\sc Tweebank v2}
Following the guidelines mentioned above, we create a new annotated Twitter treebank, which we call {\sc Tweebank v2}.

\subsubsection{Data Collection}
{\sc Tweebank v2} is built on the original data of {\sc Tweebank v1} (Kong et al., 2014, 639 tweets), along with additional 201 tweets sampled from \newcite{gimpel-EtAl:2011:ACL-HLT2011} and 2,500 tweets sampled  from the Twitter stream from February 2017 to July 2017.
The latter data source consists 147.4M English tweets which are filtered by {\it lang} attribute in the tweet JSON and {\it langid.py}\footnote{\url{https://github.com/saffsd/langid.py}} toolkit.
%The tweet source of Tweebank V2 consists of three parts. 
%The first is the original Tweebank created by~\cite{kong-EtAl:2014:EMNLP2014}, denoted as Tweebank V1.  There are 639 unique tweets in the training data of Tweebank V1, and 201 unique tweets in the data set. All of the unique tweets in Tweebank V1 are included in Tweebank V2.
%The second are 210 tweets from POS-tagged Twitter corpus of \newcite{owoputi-EtAl:2013:NAACL-HLT}, denoted as Tweebank V1 Dev. It was initially created as a development set of Tweebank V1 for hyperparameter tuning.
%Tweebank V1 Dev comprises were equally sampled from two data set, OCT27 (tweets sampled from a particular day, October 27, 2010) and DAILY 547 (one random English tweet per day from January 2011 through June 2012, 547 tweets in total). We should note that all of the Tweebank V1 tweets were also drawn from OCT27 and DAILY547, and the new tweets we extracted are not in the Tweebank V1.
%The third are 2500 tweets from the Twitter streams from February 2017 to July 2017 from ArchiveTeam,\footnote{https://archive.org} which we call Feb\_Jul\_16 corpus. The Twitter streams are in Spritzer version, which provides a 1\% random sample of public tweets everyday, and the tweets are in twitter JSON format. 
%There are xxx tweets in all the streams. We filtered them with \textit{lang} attribute in \textit{user} and used \textit{langid.py}\footnote{https://github.com/saffsd/langid.py} to pick out English tweets, which ends in xxx tweets in English. Then we sampled 2500 tweets roughly equally from these months.

\subsubsection{Annotation Process}
Our annotation process was conducted in three stages.
In the first stage, 18 researchers worked on the {\sc Tweebank v1}
proportion and created the initial annotations in one day.
\nascomment{Check:} Before annotating, they were given a tutorial overview of the UD
annotation conventions and our guidelines.
Both the guidelines and annotation
were further refined by the authors of this paper to increase
the coverage of our guideline and solve inconsistency between
different annotators during this exercise. In the second stage, a POS tagger and
parser were trained on the annotated data from the first stage,
and used to automatically analyze the sampled 2,500 tweets.  Authors 
of this paper manually corrected the parsed data. \nascomment{this is
  a little weird:  don't you have to do this before you parse?} Finally, an extra
layer of word-level normalization was manually annotated.

\begin{figure}
\centering
\small
\begin{dependency}[edge slant=2, text only label, label style=above]
	\begin{deptext}
		Olympic \& gold \& medallist \& whipped \& by \& John \& Fisher \\
	\end{deptext}
	\deproot{3}{root}
	\depedge[edge unit distance=1em]{3}{1}{amod}
    \depedge[edge unit distance=1em]{3}{2}{compound}
    \depedge[edge unit distance=1em]{3}{4}{acl}
    \depedge[edge unit distance=1em]{4}{6}{obl}
    \depedge[edge unit distance=1em]{6}{5}{case}
    \depedge[edge unit distance=1em]{6}{7}{flat}
	\deproot[edge below]{4}{root}
%	\depedge[edge below, edge unit distance=1em]{3}{1}{amod}
%	\depedge[edge below, edge unit distance=1em]{3}{2}{compound}
	\depedge[edge below, edge unit distance=1em]{4}{3}{nsubj}
%	\depedge[edge below, edge unit distance=1em]{4}{6}{obl}
%	\depedge[edge below, edge unit distance=1em]{6}{5}{case}
%	\depedge[edge below, edge unit distance=1em]{6}{7}{flat}
\end{dependency}
\caption{An example of disagreement; one annotator's parse is shown above, disagreeing arcs from the other
  annotator are shown below.}\label{fig:disagree}
\end{figure}

We report the inter-annotator agreement between the annotators
in the second stage. The agreement on POS is 96.61\%, the unlabeled
dependency agreement is 88.75\% and the labeled dependency agreement
is 84.31\%. Further analysis shows the major disagreements on POS
involve entity names (30.57\%) and topical hashtags (18.11\%).
Taking the example in Figure \ref{fig:non-syn-toks}, ``Fix you'' can
be understood as a verbal phrase but also as the name of the Coldplay's
single and tagged as proper noun. An example of a disagreement on
dependencies is shown in Figure \ref{fig:disagree}.  Depending on
whether this is an example of an empty auxiliary verb, or a clause-modified
noun, both annotations are reasonable.

@@

We present a pipeline system to parse tweets into universal
dependencies.  We evaluate each component individually, and the system
as a whole.

\subsection{Tokenizer} \label{sec:tok}
Tokenization, as the initial step of many NLP tasks, is non-trivial for
informal tweets, which include hashtags, at-mentions, and emoticons
\cite{ICWSM101540}.  Context is often required for tokenization
decisions; for example,
the asterisk (*) in {\it 4*3} is a separate token signifying
multiplication, but for the asterisk (*) in {\it sh*t}
works as a mask for censorship and should not be segmented.

We introduce a new
character-level bidirectional LSTM (bi-LSTM) sequence-labeling model
\nascomment{add cite for this kind of model}
for tokenization.
Our model takes the raw sentence and tags each character in this 
sentence as whether it is the beginning of a word.
\nascomment{check:} It is trained on the training portion of
\textsc{Tweebank v2} combined with the UD\_English training dataset.

\paragraph{Experimental results.}

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it System & $F_1$ \\
		\hline
		Stanford CoreNLP & 96.6 \\
		Twokenizer & 94.4 \\
% 		UD pipe v1.2 & 94.7 \\
		UD pipe v1.2 (same training data) & 97.3 \\
		Our bi-LSTM tokenizer & \bf 98.3 \\
		\hline
	\end{tabular}
	\caption{Tokenizer comparison on the \textsc{Tweebank v2} test set.}\label{tbl:tok-result}
\end{table}

We tested our tokenizer on the \textsc{Tweebank v2} test set. 
We report $F_1$ scores, combining precision and recall for token identification. Table \ref{tbl:tok-result} shows the
tokenization results, compared to  other available tokenizers. 
\nascomment{Check:}  The Stanford \nascomment{cite}  and Twokenizer
\nascomment{cite} systems are rule-based systems and were not adapted
to the UD tokenization scheme.
The UD pipe v1.2
\cite{straka-strakova:2017:K17-3} model was re-trained on the same
data as our system.
Our bi-LSTM tokenizer achieves the best accuracy among all these
tokenizers.  These results indicate the value of statistical modeling
in tokenization for informal texts.

\subsection{Part-of-Speech Tagger}

Part-of-speech tagging for tweets has been extensively studied \cite{ritter-EtAl:2011:EMNLP,gimpel-EtAl:2011:ACL-HLT2011,owoputi-EtAl:2013:NAACL-HLT,gui-EtAl:2017:EMNLP20172}.
On the annotation scheme designed in \S\ref{sec:pos-anno}, based on UD and adapted for
Twitter, we compared several existing systems and also two bi-LSTM systems similar
to \citet{??} \nascomment{add cite}, one using word vectors and the
other using word and character vectors.   All systems were re-trained on
the combination of the UD\_English and \textsc{Tweebank v2} training sets.

\nascomment{I wonder if we ought to give more detail about our biLSTM
  systems, here and under tokenization?  will reviewers want to know details?}

\paragraph{Experimental results.}

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it System & \it Precision \\
		\hline
%		Stanford Postagger & 65.6 \\
		Stanford CoreNLP & 90.4 \\
%		UD pipe v1.2 & 78.7 \\
		\citealp{owoputi-EtAl:2013:NAACL-HLT} (greedy) & 94.2 \\
		\citealp{owoputi-EtAl:2013:NAACL-HLT} (CRF) & \bf 95.1 \\
		\hdashline
%		UD pipe v1.2 & 83.8 \\
		\citealp{ma-hovy:2016:P16-1} & \\
		our word bi-LSTM & 89.1 \\
		our character + word bi-LSTMs & 91.4 \\
		\hline
	\end{tabular}
	\caption{POS tagger comparison on gold-standard tokens in the
          \textsc{Tweebank v2} test set. \label{tbl:pos-result}
          \nascomment{to do:  fill in Ma/Hovy}}
\end{table}

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it System & $F_1$ \\
		\hline
		Stanford CoreNLP & 92.0 \\
		our tokenizer (\S\ref{sec:tok}) & 93.6 \\
		\hline
	\end{tabular}
	\caption{\citet{owoputi-EtAl:2013:NAACL-HLT} POS tagging performance with automatic tokenization on
          the \textsc{Tweebank v2} test set. \label{tbl:pos-result-vs-tok}}
\end{table}

We tested the POS taggers on \textsc{Tweebank v2} test set.  Results
with gold-standard tokenization are shown in
Table \ref{tbl:pos-result}. The careful feature engineering in the 
POS tagger  of \citet{owoputi-EtAl:2013:NAACL-HLT} outperforms our neural network
models.  (That tagger also makes use of \citet{Brown} clusters derived
from a large collection of unannotated tweets.  Those clusters did not
improve the performance of our bi-LSTM models.)

Results of the \citet{owoputi-EtAl:2013:NAACL-HLT}  with non-greedy
inference \nascomment{check} on automatically tokenized data
are shown in  Table \ref{tbl:pos-result-vs-tok}.  We see that errors
in tokenization do propagate, but tagging performance is above 93\%
with our tokenizer.
